\documentclass{article}

\title{Spacing and Sizing Commands}
\author{htex Library}
\date{2026}

\begin{document}

\maketitle

\section{Font Size Changes}

This is \small{small text} back to normal.

This is \Large{large text} back to normal.

\tiny{Tiny text is very small}

\small{Small text}

\normalsize{Normal size}

\large{Large text}

\Large{Larger text}

\LARGE{Even larger text}

\huge{Huge text}

\Huge{Largest text}

\normalsize{Return to normal}

\section{Horizontal Spacing}

Text\quad more text with quad spacing (1em).

Text\qquad more text with qquad spacing (2em).

Text\hspace{2cm}more text with 2cm horizontal space.

Text\hspace{1em}more text with 1em horizontal space.

\section{Vertical Spacing}

First paragraph.

\vspace{1cm}

After 1cm vertical space, second paragraph.

\medskip

After medium skip.

\bigskip

After big skip.

\smallskip

After small skip.

\section{Phantom Commands}

Invisible placeholder: \phantom{This is hidden but takes space} and we continue.

Horizontal phantom: X\hphantom{hidden}Y are separated by horizontal space.

Vertical phantom: Line with \vphantom{descenders} and without descenders.

\section{Practical Examples}

Here's some alignment using phantom:

\hspace{3em}Indented text

\phantom{prefix}Aligned with phantom prefix

Text\quad\quad\quad with multiple quads for spacing

\section{Combined Spacing and Sizing}

\Large{
  Large text with spacing.
  
  \vspace{0.5cm}
  
  Continues here.
}

\normalsize{
  Normal text again.
  \hspace{2cm} with horizontal space.
}

\end{document}
